---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
After cloning the repository, I manually unzipped the data file to bypass temp storage and unzip. To load the data from that point I make a simple read_csv() call using the readr package.

```{r echo=TRUE}
library(tidyverse)
x <- read_csv("data/activity.csv")
```


## What is mean total number of steps taken per day?
Aggregate steps by day and create a histogram from the new object.

```{r echo=TRUE}
x2 <- aggregate(x$steps, list(Date=x$date), FUN=sum, na.rm = TRUE)
colnames(x2) <- c("date", "steps")
hist(x2$steps, freq = TRUE, main = "Histogram for Daily Steps", xlab = "Total Steps")
```

```{r echo=TRUE}
mean.steps <- round(mean(x2$steps), digits = 0)
median.steps <- round(median(x2$steps))
```

Mean steps per day is 9,354 and median steps per day is 10,395.

## What is the average daily activity pattern?
Aggregate the average number of steps by interval and plot it as a time series.

```{r echo=TRUE}
mean.interval <- aggregate(x$steps, by=list(interval=x$interval), FUN=mean, na.rm = TRUE)
colnames(mean.interval) <- c("interval", "steps")
plot(mean.interval$interval, mean.interval$steps, type="l", xlab="Interval", ylab="Mean Number of Steps", main="Average Daily Activity")
```

```{r echo=TRUE}
index <- which.max(mean.interval$steps)
max.interval <- mean.interval$interval[index]
```

The interval containing the maximum number of steps, on average, is interval 835.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
